Real-Time Systems

### 2013-12-16 beamer/dit-paper-presentation_v2.tex
SBESC version of DIT paper presentation

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{pgfpages}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}

\title {Real-Time Systems}
\subtitle {The Space of Feasible Execution Times for Asynchronous Periodic Task
Systems using Definitive Idle Times}
\author{Thomas~Chapeaux~\inst{1}~\inst{2} \and Paul~Rodriguez~\inst{1}~\inst{2} \and Laurent~George~\inst{2} \and Joël~Goossens~\inst{1}}
\institute[shortinst]{\inst{1} Université Libre de Bruxelles \and %
                      \inst{2} ECE Paris}
\date{July 2013}

@@

\begin{frame}
    \tableofcontents[hideothersubsections]
\end{frame}

@@

\begin{frame}
    \tableofcontents[currentsection, hideothersubsections]
\end{frame}

	\subsection{Real-time systems}

	\begin{frame}{Model}
  \begin{block}{Real-Time Systems}
  Systems with timeliness constraints. (e.g. ABS, VOD, etc)
  \end{block}
  \textbf{Model:} $\tau$ set of $n$ tasks $\tau_i = (O_i, C_i, D_i, T_i)$ generating jobs $J_{i,j}$
      \begin{itemize}
      \item $O_i$ : arrival of the first job
      \item $C_i$ : worst-case execution time (WCET)
      \item $D_i$ : relative deadline
      \item $T_i$ : time between two job arrivals
    \end{itemize}

@@

  \column{.6\textwidth} % column designated by a command
\begin{figure}[h]
\includegraphics[width=\textwidth]{figs/RTsystem_example.png}
\caption{A task system}
\label{fig:llf}
\end{figure}
  \end{columns}
\end{frame}

@@

	\begin{frame}{Feasibility}
		\begin{block}{Feasibility}
        A task set is said to be \textbf{feasible} if there exists a schedule such that every job in the task set completes before its deadline is reached.
        \end{block}

        % \begin{block}{Feasibility by a scheduling policy}
        % A task set is said to be \textbf{schedulable by a given scheduling policy} if every job in the task set completes before its deadline is reached when using this scheduling policy.
        % \end{block}

        In the uniprocessor case, the EDF (Earliest Deadline First) scheduling policy is optimal, any feasible task set is correctly scheduled by EDF.
	\end{frame}

@@

    \begin{frame}{Definition of the C-space}
        \begin{block}{C-space}
            The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any vector $C = \{ C_1, \cdots, C_{n}\}$ in it, $\tau$ is feasible.
        \end{block}

        \begin{itemize}
            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints on the $C_i$.
            \item An efficient description allows us to decide whether a system whose $O_i$, $T_i$ and $D_i$ values are known will be feasible on a given platform (which gives the $C_i$).
        \end{itemize}

@@

	\section{Previous works}

    \begin{frame}
    \tableofcontents[currentsection, hideothersubsections]
    \end{frame}

    \subsection{Demand-bound function}

    \begin{frame}{Demand-bound function feasibility test}
        \begin{block}{Demand-bound function}
            The \textbf{demand-bound function (DBF)} \cite{baruah1999generalized,
        baruah1990algorithms}
            of a task set $\tau$, denoted $\dbf{t_1, t_2}$, is
            the maximal cumulated execution time of jobs of $\tau$ contained in the
            closed interval $[t_1, t_2]$.
        \end{block}
        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i$$
        where $n_i(t_1, t_2)$ is the number of jobs of $\tau_i$ in the interval $[t_1, t_2]$.

        The following has been shown to be a necessary and sufficient condition of feasibility (called DBF test in the following): $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$

    \subsection{C-space of synchronous systems}

    \begin{frame}{Description using the DBF test}
    The DBF test gives us a set of constraints to describe the C-space
    $$\dbf{t_1, t_2} \leqslant t_2 - t_1 \; \forall t_1 \leq t_2$$

    \begin{itemize}
        \item Every constraint is linear in the $C_i$ values.
        \item We have an infinite number of constraints!
        \item Every constraint is a necessary condition of feasibility.
        \item Their conjunction is a sufficient condition of feasibility.
        % \pause
        \item $\Rightarrow$ We must find a way of removing redundancies in the constraints.
    \end{itemize}
    \end{frame}

    \begin{frame}{Removing redundancy for synchronous systems}

    The authors of \cite{george2009characterization} obtain an efficient description of the C-space by
    \begin{itemize}
        \item Removing constraints in which $t_1 > 0$
        \item Removing constraints in which $t_2$ is not a deadline or $t_2 > H$ (where $H = LCM(T_i)$)
    \end{itemize}

    ~\\
    % \pause

    They also define the notion of \textbf{definitive idle times (DIT)} and show that the first one happens at a time $0 < t_d \leqslant H$. Finally they show that all constraints where $t_2 > t_d$ are also redundant.

    ~\\
    % \pause

    The remaining constraints are thus the DBF test on intervals $[0, t]$, where $t$ is a deadline and $0 < t \leqslant t_d$. The remaining redundancies are removed by an algorithm based on the simplex.

    % \subsection{Cyclic Idle Times}

    % \begin{frame}{Cyclic Idle Times}

    % \end{frame}

@@

	In the article, we
    \begin{itemize}
        \item Introduce the notion of \textbf{first periodic DIT (FPDIT)} as a generalization of the notion of DIT
        \item Provide an algorithm to find an efficient description of the C-space for any periodic constrained deadline systems
        \item Quantify the feasibility gain of random offsets in terms of C-space volume ratio.
    \end{itemize}

@@

    \begin{frame}
        \tableofcontents[currentsection, hideothersubsections]
    \end{frame}

@@

        The FPDIT is the smallest $t_d$ such as:
       \[
            \begin{array}{l}
                \forall \tau_i \in \tau, \exists a_i \in [D_i,T_i] \; :\\
                \left\{
                    \begin{array}{l}
                        t_d > O_i \\
                        t_d - O_i \equiv a_i \; (mod \; T_i)
                        \\
                    \end{array}
                \right.
            \end{array}
        \]

@@

	\subsection{Finding the FPDIT value}

    \begin{frame}{Finding the FPDIT value - Gauss's Algorithm}
        For given values of $a_i$, if the periods are pairwise coprime, the value of a DIT is given by :

        \begin{algorithm}[H]
            \caption{Gauss's CRP Algorithm}
            \label{alg:algoCRP}
            \begin{algorithmic}[1]
                \REQUIRE $C$ the set of constraint $c$ : $\left( t_d \equiv x(c) \; (\operatorname{mod} \; p(c)) \right)$
                \REQUIRE $H$ the hyperperiod of the system
                \FORALL{$c \in C$}
                    \STATE $Mc \leftarrow \frac{H}{p(c)}$
                    \STATE $invMc \leftarrow Mc^{-1} \; (mod \; p(c))$
                    \STATE $e_c \leftarrow Mc \cdot invMc$
                \ENDFOR
                \RETURN $\sum\limits_{c \in C}{x(c) \cdot e_c} \; (mod \; H)$
            \end{algorithmic}
        \end{algorithm}

    \begin{frame}{Non-pairwise co-prime moduli}
        If the periods are non-pairwise co-prime, the system has a DIT for given values of $a_i$ if and only if the following condition is respected:
        \[
            a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
            T_j)) \; \forall i,j
        \]
		The CRP is then solved by constructing an equivalent system with pairwise co-prime moduli.\\

		In the asynchronous case, it is thus possible to have systems where no FPDIT exists.
        %Then each equation $t_d \equiv x \; (\operatorname{mod} \; p)$ with $p = p_1^{b_1} \cdots p_k^{b_k}$ (where each $p_i$ is prime), can be replaced by the system:

       %\[
       %     \begin{array}{l}
       %         \left\{
       %             \begin{array}{l}
       %                  t_d \equiv x \; (mod \; p_1^{b_1}) \\
       %                  \cdots \\
       %                  t_d \equiv x \; (mod \; p_k^{b_k})
       %             \end{array}
       %         \right.
       %     \end{array}
       % \]

        %Equations with the same $p_i$ can be replaced by only the one of highest $b_i$. The new system now has pairwise co-prime moduli.

@@

    \begin{columns}[c]
        \column{0.4\textwidth}

        Systems were generated by
        \begin{itemize}
            \item Choosing $T_i$ in [5, 20]
            \item Choosing $O_i$ in [0, $H$]
            \item Choosing $D_i$ in [$T_i - CDF * T_i$, $T_i$]
        \end{itemize}

        \column{0.6\textwidth}
        \includegraphics[width=1.2\textwidth]{figs/nofpdit_5.png}

@@

@@

	\begin{frame}{Initial description}
		The C-space is still accurately described by the following infinite number of constraints:

        $$\dbf{t_1, t_2} \leq t_2 - t_1 \; \forall t_1 \leqslant  t_2$$

        As in the synchronous case,
        \begin{itemize}
            \item Every constraint is a necessary condition.
            \item Their conjunction is a sufficient condition.
            \item Most of them are redundant.
        \end{itemize}
        However the method used to remove redundancies will be different.
	\end{frame}

@@

    \begin{frame}{Feasibility study interval}

        The authors of \cite{leung1982complexity} have shown that for asynchronous systems, it sufficient to check the DBF test in intervals $[t_1, t_2]$ where $$O_{max} \leqslant t_1 < t_2 \leqslant O_{max} + 2 \cdot H$$

        Indeed, it can be shown that at instant $O_{max} + 2 \cdot H$ at the latest, the system enters a periodic behavior. If follows that if no deadlines have been missed before it, no future deadline misses can occur.

@@

    \begin{frame}{Arrivals and deadlines}

        By definition of the demand-bound function, it is sufficient to check only intervals where $t_1$ is an arrival and $t_2$ is a deadline.

        \begin{block}{Demand-bound function}
            The \textbf{demand-bound function (DBF)}
            defined for a task set $\tau$ in a time interval $[t_1, t_2]$, denoted $\dbf{t_1, t_2}$, is
            the maximal cumulated execution time of jobs of $\tau$ contained in the
            closed interval $[t_1, t_2]$.
        \end{block}

        The authors of \cite{choquet2004minimal} define the notion of \emph{cyclic idle times}, the first of which marks the start of the periodic behavior of the system. They prove that if $t_c$ is a cyclic idle time and there are no deadline miss in the interval $[t_c, t_c + H]$, then the system is feasible.

        However the existence and position of the cyclic idle times depend on the values of the $C_i$ and are therefore not accessible when describing the C-space.

        By definition, if the FPDIT exists it will also be a cyclic idle time. It follows that the interval $[t_d, t_d + H]$ is sufficient.

    \begin{frame}{Redundancy as an ILP (I)}

    We can define the redundancy of a linear constraint $DBF' \cdot C \leqslant t_2 - t_1$ with regards to the set of $k$ linear constraints $DBF \cdot C \leqslant T$ as the following Integer Linear Problem (ILP):

        \begin{block}{Redundancy ILP}

        % \begin{center}
        $z = \max \left( DBF' \cdot C \right)$

        s.t. $DBF  \cdot C \leq T$

        %$
        % \begin{array}{ccccc}
        % DBF  & \cdot & C &\leq & T \\
        % DBF' & \cdot & C &\leq & t_2 - t_1 + 1
        % \end{array}
        %$
        % \end{center}

        \end{block}

        \column{0.4\textwidth}

        % \begin{center}with\end{center}
        \[
          \begin{array}{ccc}
            DBF & : & [n,k] \text{ matrix}\\
            DBF' \; \text{and} \; T & : & [n,1] \text{ matrices}\\
            C & : & [1,n] \text{ matrix}\\
            t_2 \; \text{and} \; t_1 & : & \text{integers}
          \end{array}
        \]
    \end{columns}
        \begin{itemize}
            \item If $z \leqslant t_2 - t_1$, the constraint is redundant
            % \item Can be solved with a branch-and-bound approach
            \item Complexity (one test): exponential in the size of the set
            \item Each constraint of the set must be tested
        \end{itemize}

    \begin{frame}{Redundancy as an ILP (II)}

        \begin{algorithm}[H]
            \caption{Removing redundant constraints}
            \label{alg:pruneCspace}
          \begin{algorithmic}[1]
            \STATE $CSPACE$ : set of constraints
            \STATE $S \leftarrow \emptyset$
            \STATE \COMMENT{$1^{st}$ pass: test each $cstr$ against previous ones}
            \FOR{$cstr$ \textbf{in} $CSPACE$}
              \IF {$cstr$ is not redundant w.r.t. $S$}
                \STATE $S.push(cstr)$
              \ENDIF
            \ENDFOR
            \STATE \COMMENT{$2^{nd}$ pass: test remaining $cstr$ against every other}
            \FOR{$cstr$ \textbf{in} $S$}
              \STATE $cstr$ = $S.pop()$
              \IF {$cstr$ is not redundant w.r.t. $S$}
                \STATE $S.push(cstr)$
              \ENDIF
            \ENDFOR
            \RETURN{S}
            \end{algorithmic}
        \end{algorithm}
    \end{frame}

	\begin{frame}{Redundancy removal summary}

		To summarize, a finite number of constraints is given by applying the DBF test to intervals:
		\begin{itemize}
			\item beginning at a job arrival,
			\item ending at a job deadline,
			\item strictly contained in
			\begin{itemize}
				\item $[t_d, t_d + H]$ if there exists a FPDIT at $t_d$
				\item $[O_{max}, O_{max} + 2 \cdot H]$ otherwise
			\end{itemize}
		\end{itemize}

		Remaining redundancies are removed with a general ILP approach.

    \subsection{Example}

    \begin{frame}{Example (I)}
        \[
        \begin{array}{|r|c|c|c|c|}
         \hline
          & O_i & C_i & D_i & T_i \\
         \hline
         \tau_1 & 8 & C_1 & 7 & 15\\
         \hline
         \tau_2 & 0 & C_2 & 2 & 5\\
         \hline
        \end{array}
        \]

@@

@@

    We remove the remaining redundancies with the ILP approach:
    $$
        \left\{
            \begin{array}{cccccc}
                & & & C_2 & \leqslant & 2 \\
                C_1 & + & & C_2 & \leqslant & 7
            \end{array}
        \right.
    $$

@@

        We want to express the feasibility gain of random offsets as the ratio

@@

            \begin{itemize}
                \item Around 10\% of amelioration for high-utilization systems
                \item Gain not highly dependent of utilization or CDF
            \end{itemize}

@@

@@

    \begin{itemize}
        \item Further ways of reducing redundancy before applying the ILP approach
        \item Other metrics to quantify the quality of the C-space
        \item Extension to multiprocessor scheduling
    \end{itemize}

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{pgfpages}
\usepackage{algorithm}
\usepackage{color}
\usepackage[noend]{algorithmic}

\title {Real-Time Systems}
\subtitle {The Space of Feasible Execution Times for Asynchronous Periodic Task
Systems using Definitive Idle Times}
\author{Thomas~Chapeaux~\inst{1}~\inst{2} \and Paul~Rodriguez~\inst{1}~\inst{2} \and Laurent~George~\inst{2} \and Joël~Goossens~\inst{1}}
\institute[shortinst]{\inst{1} Université Libre de Bruxelles \\ Belgium \and %
                      \inst{2} ECE Paris \\ France}
\date{July 2013}

@@

\begin{frame}
    \tableofcontents[hideallsubsections]
\end{frame}

@@

\begin{frame}
    \tableofcontents[currentsection, hideallsubsections]
\end{frame}

% 	\subsection{Real-time systems}

	\begin{frame}{Model}
  \begin{block}{Real-Time Systems}
  Systems with timeliness constraints. (e.g. ABS, VOD, etc)
  \end{block}
  \textbf{Model:} $\tau$ set of $n$ tasks $\tau_i = (O_i, C_i, D_i, T_i)$ generating jobs $J_{i,j}$
      \begin{itemize}
      \item $O_i$ : arrival of the first job
      \item $C_i$ : execution time
      \item $D_i$ : relative deadline
      \item $T_i$ : time between two job arrivals
    \end{itemize}
  We consider periodic systems with constrained deadline on uniprocessor platforms.

@@

  \column{.6\textwidth} % column designated by a command
\begin{figure}[h]
\includegraphics[width=0.7\textwidth]{figs/RTsystem_example.png}
\label{fig:llf}
\end{figure}
  \end{columns}

@@

    \subsection{Motivation}

    \begin{frame}{Motivation}

        \begin{block}{Feasibility}
        A task set is said to be \textbf{feasible} if there exists a schedule such that every job in the task set completes before its deadline is reached.
        \end{block}

        \begin{itemize}
            % \begin{columns}[c]
            % \column{.1\textwidth}
            % \column{.4\textwidth}
            %     \begin{tabular}{|r|c|c|c|c|}
            %      \hline
            %       & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
            %      \hline
            %      $\tau_1$ & 1 & 2 & 6 & 10\\
            %      \hline
            %      $\tau_2$ & 0 & 3 & 5 & 5\\
            %      \hline
            %     \end{tabular}
            % \column{.5\textwidth}
            %     \includegraphics[width=\textwidth]{figs/RTsystem_example.png}
            % \end{columns}
            \item When implementing a system on different platform, the $C_i$ values may vary. How can we efficiently check if a system is feasible on a given platform?

            \item Most feasibility tests assume specific values of the $C_i$, which means that they must be applied once for each candidate platform.

            \item Our solution is to provide a description of the space of feasible execution times which can be  used to efficiently test any platform.
        \end{itemize}
    \end{frame}

@@

    \begin{frame}{Definition of the C-space}
        \begin{block}{C-space}
            The \textbf{C-space} of a task system $\tau$ is a region of $n$ dimensions (where each dimension denotes the possible $C_i$ of a task of $\tau$) such that for any point $C = \{ C_1, \cdots, C_{n}\}$ in it, $\tau$ is feasible.
        \end{block}

\begin{columns}[c]
    \column{0.5\textwidth}
        \begin{itemize}
            \item A region of $\mathbb{N}_0^n$ such as the C-space is described by a set of parametric linear constraints on the $C_i$.
            \item Example:
            \begin{tabular}{|r|c|c|c|c|}
             \hline
              & $O_i$ & $C_i$ & $D_i$ & $T_i$ \\
             \hline
             $\tau_1$ & 1 & ? & 6 & 10\\
             \hline
             $\tau_2$ & 0 & ? & 5 & 5\\
             \hline
            \end{tabular}
        \end{itemize}
    \column{0.5\textwidth}
        \begin{center}
        \begin{figure}
            \includegraphics[width=0.9\textwidth]{figs/cspace_example_2.png}
            \caption{C-space containing 17 possible $C_i$ values}
        \end{figure}
        \end{center}

    \end{columns}
    \end{frame}

    \begin{frame}{C-space of synchronous systems}

    \begin{itemize}
        \item The authors of \cite{george2009characterization} obtain an efficient description of the C-space of synchronous systems based on the DBF test\cite{baruah1990algorithms}, a necessary and sufficient condition of feasibility for constrained deadline systems.
        \item However, synchronous systems are a worst-case with regards to feasibility, i.e. some unfeasible synchronous systems become feasible if specific offsets are added. In the literature (e.g. \cite{goossens2003scheduling}), the benefits of offsets are confirmed.
        \item This motivates a description of the C-space for asynchronous systems.

    \end{itemize}

% a necessary and sufficient condition of feasibility:$$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leqslant t_2 - t_1 \; \; \forall t_1 \leq t_2$$
%         where $n_i(t_1, t_2)$ is the number of jobs of $\tau_i$ in the interval $[t_1, t_2]$.

%     ~\\

%     The description is given by the DBF test on intervals $[0, t]$, where $t$ is a deadline and $0 < t \leqslant H$ (with $H = LCM(T_i)$).

%     ~\\

%     The remaining redundancies are removed by an algorithm based on the simplex (with exponential worst-case complexity).

@@

@@

	In the article, we
    \begin{itemize}
        \item Introduce the notion of \textbf{First Periodic Definitive Idle Times}, which provides a study interval independent of the execution times.
        \item Extend the description of the C-space for asynchronous periodic constrained deadline systems
        \item Quantify the feasibility gain of random offsets in terms of C-space volume ratio.
    \end{itemize}

@@

    \begin{frame}
        \tableofcontents[currentsection, hideallsubsections]
    \end{frame}

@@

        \includegraphics<1>[width=\textwidth]{figs/DIT_example.png}
        \includegraphics<2>[width=\textwidth]{figs/DIT_example_2.png}

        The FPDIT is the smallest $t_d$ such as:
       \[
            \begin{array}{l}
                \forall \tau_i \in \tau, \exists a_i \in [D_i,T_i] \; :\\
                \left\{
                    \begin{array}{l}
                        t_d > O_i \\
                        t_d - O_i \equiv a_i \; (mod \; T_i)
                        \\
                    \end{array}
                \right.
            \end{array}
        \]
        \end{columns}

@@

    \subsection{Possible non-existence}

    \begin{frame}{Possible non-existence}

    \begin{itemize}
        \item In asynchronous systems, it is possible for a system to not have any FPDIT. Example:
        \begin{center}
            \includegraphics[width=.6\textwidth]{figs/nofpdit_example.png}
        \end{center}
        \item In fact, a system has a FPDIT if and only if the following condition is fulfilled for some value of $a_i$:

            \[
                a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
                T_j)) \; \forall i,j
            \]

        \item Note that in synchronous systems ($O_i = 0 \; \forall i$), the hyperiod $H = LCM(T_i)$ is always a DIT.
    \end{itemize}

@@

    \begin{columns}[c]
        \column{0.6\textwidth}

        \includegraphics[width=1\textwidth]{figs/nofpdit_5.png}

        \column{0.4\textwidth}
        Systems were generated by
        \begin{itemize}
            \item Choosing $T_i$ in [5, 20]
            \item Choosing $O_i$ in [0, $H$]
            \item Choosing $D_i$ in [$T_i - CDF * T_i$, $T_i$]
        \end{itemize}

@@

    FPDIT are less frequent in systems with a high number of tasks or a low CDF.

@@

	\begin{frame}{Initial description}
		The C-space is accurately described by the following infinite number of constraints:

        $$\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall t_1 \leqslant  t_2$$
        where $n_i(t_1, t_2)$ is the number of jobs of $\tau_i$ whose release time and deadline are both strictly included the interval $[t_1, t_2]$.

        Based on previous results, a sufficient description is given by intervals $[t_1, t_2]$ where
        \begin{itemize}
            \item $t_1$ is an arrival
            \item $t_2$ is a deadline
            \item $0 \leqslant t_1 < t_2 \leqslant O_{max} + 2 \cdot H$ (where $H = LCM(T_i)$)
        \end{itemize}
	\end{frame}

@@

        If the FPDIT exists, we can use the constraints given by the DBF test on intervals $[t_1, t_2]$ such that
        $$t_d \leqslant t_1 < t_2 \leqslant t_d + H$$
        which is a smaller interval than $[0, O_{max} + 2 \cdot H]$

@@

    \begin{frame}{Redundancy as an ILP}

    We can define the redundancy of a linear constraint with regards to the set of $k$ linear constraints as an Integer Linear Problem.

        \begin{itemize}
            % \item If $z \leqslant t_2 - t_1$, the constraint is redundant
            % \item Can be solved with a branch-and-bound approach
            \item Each constraint of the set must be tested
            \item The worst-case complexity of each test is exponential in $k$
            \item In the paper, we propose a two-pass approach to reduce the number of constraints.
        \end{itemize}

    \end{frame}
    \subsection{Example}

    \begin{frame}{Example (I)}
        \[
        \begin{array}{|r|c|c|c|c|}
         \hline
          & O_i & C_i & D_i & T_i \\
         \hline
         \tau_2 & 0 & C_2 & 2 & 5\\
         \hline
         \tau_1 & 8 & C_1 & 7 & 15\\
         \hline
        \end{array}
        \]

@@

    \begin{frame}{Example (II) ILP first pass}

    \begin{columns}[c]
    \column{.45\textwidth}
        \begin{center}
            \includegraphics[width=\textwidth]{figs/CspaceExampleArrDead_restricted.png}
        \end{center}

        The DBF test:
        $$\sum_{i=1}^{n} n_i(t_1, t_2) \cdot C_i \leqslant t_2 - t_1 \; \; \forall t_1 \leq t_2$$

    \column{.55\textwidth}
        \[
        \left\{
            \begin{array}{cccccccc}
                0 & C_1 & + & 1 & C_2 & \leqslant & 17 - 15 & (x) \\
                \pause
                    \color{gray} 0 &
                    \color{gray} C_1 &
                    \color{gray} + &
                    \color{gray} 2 &
                    \color{gray} C_2 &
                    \color{gray} \leqslant &
                    \color{gray} 22 - 15 & \\
                \pause
                    \color{gray} 0 &
                    \color{gray} C_1 &
                    \color{gray} + &
                    \color{gray} 3 &
                    \color{gray} C_2 &
                    \color{gray} \leqslant &
                    \color{gray} 27 - 15 & \\
                \pause
                1 & C_1 & + & 3 & C_2 & \leqslant & 30 - 15 & (x) \\
                \pause
                    \color{gray} 0 &
                    \color{gray} C_1 &
                    \color{gray} + &
                    \color{gray} 1 &
                    \color{gray} C_2 &
                    \color{gray} \leqslant &
                    \color{gray} 22 - 20 & \\
                    \color{gray} 0 &
                    \color{gray} C_1 &
                    \color{gray} + &
                    \color{gray} 2 &
                    \color{gray} C_2 &
                    \color{gray} \leqslant &
                    \color{gray} 27 - 20 & \\
                1 & C_1 & + & 2 & C_2 & \leqslant & 30 - 20 & (x) \\
                    \color{gray} 0 &
                    \color{gray} C_1 &
                    \color{gray} + &
                    \color{gray} 1 &
                    \color{gray} C_2 &
                    \color{gray} \leqslant &
                    \color{gray} 27 - 23 & \\
                1 & C_1 & + & 1 & C_2 & \leqslant & 30 - 23 & (x) \\
                    \color{gray} 0 &
                    \color{gray} C_1 &
                    \color{gray} + &
                    \color{gray} 1 &
                    \color{gray} C_2 &
                    \color{gray} \leqslant &
                    \color{gray} 27 - 25 & \\
                    \color{gray} 0 &
                    \color{gray} C_1 &
                    \color{gray} + &
                    \color{gray} 1 &
                    \color{gray} C_2 &
                    \color{gray} \leqslant &
                    \color{gray} 30 - 25 & \\
            \end{array}
        \right.
        \]
    \end{columns}
    \end{frame}

@@

    We remove the remaining redundancies with a second exhaustive pass:
    $$
        \left\{
            \begin{array}{cccccc}
                & & & C_2 & \leqslant & 2 \\
                C_1 & + & & C_2 & \leqslant & 7
            \end{array}
        \right.
    $$

@@

        Because the synchronous release is known to be the worst-case feasibility-wise, we know that random offset can only improve the feasibility of a system.

        We express this feasibility gain given as the ratio

@@

            \begin{itemize}
                \item Around 10\% of improvement for high-utilization systems
                \item Gain not highly dependent of utilization or CDF
                \item For random offsets!
            \end{itemize}

@@

    \begin{frame}
        \tableofcontents[currentsection, hideallsubsections]
    \end{frame}

@@

    \begin{itemize}
        \item Further ways of reducing redundancy before applying the ILP approach: We often a lot of constraints before applying the ILP approach and far less afterwards. It is our belief that further theoretical results would allow to remove a lot of redundant constraints beforehand.
        \item Other metrics to quantify the quality of the C-space: Rather than the volume of the C-space, a study of the size or the minimal distance of its border may be more relevant.
        \item Using the C-space to study the impact of offsets on feasibility. Are there \emph{optimal} offset values for a given system?
        %\item Extension to multiprocessor scheduling: The values of the DITs do not depend on the number of processor.
    \end{itemize}

\begin{frame}

    \begin{center}
    \huge Abrigado!

    \normalsize Any questions?
    \end{center}
